A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Trim todos were not doing
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1005 43ef1190-90fd-4dd7-a769-d0121f02b80e

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only contain generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints.\todo{Where and how}

@@

We also note that prohibition of SPARQL results caching is rare,
amongst the servers that expose caching headers, it is common
that the result may be cached for some minutes.\todo{more to point
  out?}

@@

We already used \httph{Last-Modified} to compute heuristic lifetime
in Section~\ref{sec:simplefresh} for 554 resources.\todo{really needed?}

@@

We then sought to classify resources into the categories ``endpoint''
for SPARQL endpoints, ``vocabulary'' for ontologies, ``dataset'' for
datasets that may contain further descriptions of several resources,
or simply ``inforesources'' for those that did not fit in the above
classes. To do so, we classified based on certain predicates and
classes, see table\todo{create table}. Additionally, URIs derived from
prefix.cc were classified as ``vocabulary'' and those from SPARQLES as
``endpoint''.

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.\todo{say how many requests failed? It was a lot}
\end{subappendices}

>>>>

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only contain generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints.

@@

We also note that prohibition of SPARQL results caching is rare,
amongst the servers that expose caching headers, it is common
that the result may be cached for some minutes.

@@

@@

We then sought to classify resources into the categories ``endpoint''
for SPARQL endpoints, ``vocabulary'' for ontologies, ``dataset'' for
datasets that may contain further descriptions of several resources,
or simply ``inforesources'' for those that did not fit in the above
classes. To do so, we classified based on certain predicates and
classes. Additionally, URIs derived from prefix.cc were classified as
``vocabulary'' and those from SPARQLES as ``endpoint''.

@@

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.
\end{subappendices}
